Effects of the body force on the evacuation dynamics

### 2019-12-26 paper.tex
agregue el diagrama fundamental actualizado

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nocomp.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_comp.eps}\label{flow_density_comp}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}

>>>>

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_comp}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}
